### 2019-05-07 sections/semantics.tex
add github link

The semantics have been implemented in the Idris programming language \cite{journals/jfp/Brady13}.
We use techniques presented by \textcite{journals/entcs/JaskelioffGH11}, \textcite{journals/jfp/Swierstra08}, and \textcite{school/maktoberdorf/PeytonJones01}.
% Such an implementation increases the confidence in the correctness and completeness of the semantics.
The source code can be found on GitHub.\footnote{\url{http://github.com/XXX/XXX}}
% A proof of concept implementation in Haskell is also available, showing that \TOPHAT can be implemented without dependent types.
A command-line interface is part of this implementation.
It prompts users to type input events, which get parsed and processed by the interaction semantics.

>>>>

The semantics have been implemented in the Haskell programming language \cite{marlow2010haskell}.
We use techniques presented by \textcite{journals/entcs/JaskelioffGH11}, \textcite{journals/jfp/Swierstra08}, and \textcite{school/maktoberdorf/PeytonJones01}.
% Such an implementation increases the confidence in the correctness and completeness of the semantics.
The source code can be found on GitHub.\footnote{\url{https://github.com/timjs/tophat-haskell}}
% A proof of concept implementation in Haskell is also available, showing that \TOPHAT can be implemented without dependent types.
A command-line interface is part of this implementation.
It prompts users to type input events, which get parsed and processed by the interaction semantics.
